---
title: "p8105_hs3393_hw6"
author: "Haochen Sun"
date: "2022-11-29"
output: github_document
---

```{r pload packages, message=FALSE}
library(tidyverse)
library(ggplot2)
library(modelr)


knitr::opts_chunk$set(
  fig.width = 5,
  out.width = "60%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

```

## Problem 1
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())

# linear regression argument by bootstrap

boot_result <- weather_df %>% 
  bootstrap(n = 5000) %>% 
  mutate(
    model = map(strap, ~lm(tmax ~ tmin, data = .x)),
    result = map(model, broom::tidy),
    result2 = map(model, broom::glance)
  )

conf_result <- boot_result %>% 
  unnest(result) %>% 
  select(term, estimate, result2) %>% 
  unnest(result2) %>%  # two steps of unnest because some variable names overlap
  select(term, estimate, r.squared) %>% 
  pivot_wider(names_from = term, values_from = estimate) %>% 
  rename(b0 = `(Intercept)`,
         b1 = tmin) %>% 
  mutate(log_b0b1 = log(b0*b1)) %>% 
  summarise(
    rsquare_ci_lower = quantile(r.squared, 0.025),
    rsquare_ci_upper = quantile(r.squared, 0.975),
    log_b0b1_ci_lower = 
      quantile(log_b0b1, 0.025),
    log_b0b1_ci_upper = 
      quantile(log_b0b1, 0.975)
  ) %>% 
  mutate(across(where(is.numeric), round, 4)) # save 4 digits

```

Therefore, we can see that the 95% confidence interval for $\hat{r^2}$ is (`r pull(conf_result, rsquare_ci_lower)`, `r pull(conf_result, rsquare_ci_upper)` ), the 95% confidence interval for $log(\hat{\beta_0}*\hat{\beta_1})$ is (`r pull(conf_result, log_b0b1_ci_lower)`, `r pull(conf_result, log_b0b1_ci_upper)`).

## problem 2
```{r}
data <- read_csv("homicide-data.csv") %>% 
  janitor::clean_names() %>%
  unite("city_state", c(city, state), sep = ", ", remove = F) %>%
  filter(!city_state %in% c("Dallas, TX", "Phoenix, AZ", "Kansas City, MO", "Tulsa, AL")) %>% 
  mutate(solve = if_else(
    disposition != "Closed by arrest",
    true = 0, false = 1
  )) %>% # 0 means the case is unsolved 
    filter(victim_race %in% c("Black", "White")) %>% 
  mutate(victim_age =  as.numeric(victim_age))

log_model <- baltimore <- data %>% 
  filter(city_state == "Baltimore, MD") %>% 
  glm(solve ~ victim_age + victim_sex + victim_race, data = .,family = binomial())

model_result <- log_model %>%
  broom::tidy() %>% 
  mutate(OR = exp(estimate)) %>% 
  mutate(lower = exp(confint(log_model)[,1]),
         upper = exp(confint(log_model)[,2])
  )
```

The estimated odds ratio for solving homicides comparing male victims to victims is `r model_result["victim_sexMale","OR"]`, the 95% confidence interval for it is (`r model_result["victim_sexMale","lower"]`, `rmodel_result["victim_sexMale","upper"]`). 

```{r}
# Glm for all cities

glm_model <- data %>% 
  nest(data = -city_state)
  
```

